\Title

### 2020-03-09 manuscript/manuscript.tex
Remove forgotten textbf on table
Replace bellow for below

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}

@@

\num{1e3}

@@

The \emph{regular grid} creates an homogeneous distribution of point sources
bellow the surveyed region.
The distance between sources is controlled by the grid spacing parameter.
Keeping the boundaries of the grid constant, reducing the spacing increases the
number of sources.

The \emph{source beneath data} layout locates one source bellow each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source beneath data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source beneath data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

@@

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-median-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source bellow each block averaged coordinate.
        (see Fig.~\ref{fig:block-median-sources}(c)).
\end{enumerate}

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source beneath data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@

One possible solution is to locate each source bellow its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.

In case our survey presents heavily clustered data points on some areas, we may
want the sources bellow that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth-types}(c)).
So, the depth of the sources can be computed as follows:

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

@@

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic ground survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestGroundSourceBellowDataConstantDepthDepth
                   & \BestGroundBlockMedianSourcesConstantDepthDepth
                   & \BestGroundGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
                     & \BestGroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestGroundGridSourcesConstantDepthPad \\
        Damping & \BestGroundSourceBellowDataConstantDepthDamping
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataConstantDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBellowDataRelativeDepthDepth
                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestGroundSourceBellowDataRelativeDepthDamping
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataRelativeDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBellowDataVariableDepthDepth
                   & \BestGroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestGroundSourceBellowDataVariableDepthDepthFactor
                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestGroundSourceBellowDataVariableDepthKNearest
                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestGroundSourceBellowDataVariableDepthDamping
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBellowDataVariableDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic airborne survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBellowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBellowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBellowDataRelativeDepthDepth
                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestAirborneSourceBellowDataRelativeDepthDamping
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataRelativeDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBellowDataVariableDepthDepth
                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestAirborneSourceBellowDataVariableDepthDepthFactor
                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestAirborneSourceBellowDataVariableDepthKNearest
                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestAirborneSourceBellowDataVariableDepthDamping
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBellowDataVariableDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                  \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                  \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                  \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                  \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                  \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                  \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                  \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                  \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                  \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                  \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                  \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \GroundGridSourcesConstantDepthDepth
                      \GroundGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \GroundGridSourcesConstantDepthSpacing
                      \GroundGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                     \GroundGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \GroundGridSourcesConstantDepthDamping
                      \GroundGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \AirborneGridSourcesConstantDepthDepth
                      \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \AirborneGridSourcesConstantDepthSpacing
                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                      \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                      \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

@@

@@

The \emph{regular grid} creates an homogeneous distribution of point sources
below the surveyed region.
The distance between sources is controlled by the grid spacing parameter.
Keeping the boundaries of the grid constant, reducing the spacing increases the
number of sources.

The \emph{source below data} layout locates one source below each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source below data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source below data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

@@

\begin{enumerate}
    \item Dividing the region in blocks of equal size. The size of the blocks
        is controlled by a \emph{spacing} parameter.
        (see Fig.~\ref{fig:block-median-sources}(a)-(b)).
    \item Computing the median location of the observation points that fall
        inside each block. Blocks without any observation point are ignored.
    \item Locating one point source below each block averaged coordinate.
        (see Fig.~\ref{fig:block-median-sources}(c)).
\end{enumerate}

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source below data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@

One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth-types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.

In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth-types}(c)).
So, the depth of the sources can be computed as follows:

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

@@

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic ground survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestGroundSourceBelowDataConstantDepthDepth
                   & \BestGroundBlockMedianSourcesConstantDepthDepth
                   & \BestGroundGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
                     & \BestGroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestGroundGridSourcesConstantDepthPad \\
        Damping & \BestGroundSourceBelowDataConstantDepthDamping
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataConstantDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBelowDataRelativeDepthDepth
                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestGroundSourceBelowDataRelativeDepthDamping
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataRelativeDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBelowDataVariableDepthDepth
                   & \BestGroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestGroundSourceBelowDataVariableDepthDepthFactor
                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestGroundSourceBelowDataVariableDepthKNearest
                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestGroundSourceBelowDataVariableDepthDamping
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataVariableDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic airborne survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        R$^2$ score & \BestAirborneSourceBelowDataConstantDepthScore
                    & \BestAirborneBlockMedianSourcesConstantDepthScore
                    & \BestAirborneGridSourcesConstantDepthScore \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBelowDataRelativeDepthDepth
                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataRelativeDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBelowDataVariableDepthDepth
                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestAirborneSourceBelowDataVariableDepthKNearest
                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestAirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataVariableDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \GroundSourceBelowDataConstantDepthDepth
                   & \GroundBlockMedianSourcesConstantDepthDepth
                   & \GroundGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesConstantDepthSpacing
                     & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBelowDataRelativeDepthDepth
                   & \GroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBelowDataVariableDepthDepth
                   & \GroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \GroundSourceBelowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBelowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \AirborneSourceBelowDataConstantDepthDepth
                   & \AirborneBlockMedianSourcesConstantDepthDepth
                   & \AirborneGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesConstantDepthSpacing
                     & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBelowDataRelativeDepthDepth
                   & \AirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesRelativeDepthSpacing
                     & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBelowDataVariableDepthDepth
                   & \AirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \AirborneSourceBelowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBelowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}
